---
title: "My 2017 Strava Data"
output: md_document
---

After seeing some tweets about Marcus Volz's [R Strava package](https://github.com/marcusvolz/strava/)(and some interesting run visualizations), I decided I wanted to give it a try for my 2017 activity data. This is perfect timing since this is the first year I've been pretty consistent uploading my bike/run data.

I began with the same steps from Marcus' github page to get your bulk strava data:

### Bulk Export from Strava
1. Log in to Strava
2. Select "Settings" from the main drop-down menu at top right of the screen
3. Select "Download all your activities" from lower right of screen
4. Wait for an email to be sent
5. Click the link in email to download zipped folder containing activities
6. Unzip files

### Install packages
```{r}
install.packages(c("devtools", "mapproj", "tidyverse"))
devtools::install_github("marcusvolz/strava")
```

### Load packages
```{r}
library(strava)
library(tidyverse)
```

### Prep Data
Since I am interested in 2017 data, I'm going to start by trimming the data to just last year. The `process_data` function converts the list of .gpx files into a dataframe. 
```{r}
data <- process_data(<gpx file path>)
glimpse(data)
```

